
### Import libraries
```{r}
options(scipen=999)
library(haven)
library(dplyr)
library(tidycensus)
library(janitor)
library(purrr)
```

## Setdirectory 

```{r}
path = "C:/Users/padu/Desktop/IndexResearch/"
```

# List fips for Geography of interest. Atlanta and Charlotte 

```{r}
## North Carolina Counties 
NCcounty = lst(119)

#Georgia Counties
GAcounty = lst(051, 245, 059, 121,089,067,063,135,113,097)
```

#Create search to preview variables. The year we are interested in is 2019. The dataset of interest is ACS data

```{r}
Search <- load_variables(year = 2019, dataset = "acs5", cache = TRUE)
View(Search)
```

### Preview 

```{r}

Preview <- get_acs(geography = "tract", year = 2019, variables = "B25063_001", state = "NC", county = NCcounty ,survey = "acs5", geometry = FALSE, output = "wide")
View(Preview)

```

#### GrossRent

## North Carolina
```{r}
NC <- get_acs(geography = "tract", year = 2019, variables = c(Totalrent = "B25058_001"), state = "NC", county = NCcounty ,survey = "acs5", geometry = FALSE, output = "wide")
View(NC)
```
## Poverty -- % Individuals below poverty under .05 


```{r}
NC <- get_acs(geography = "tract", year = 2019, variables = c(PovertyTotal = "C17002_001",
                                                              PovertyUnder5_0 = "C17002_002",
                                                              
                                                              ), state = "NC", county = NCcounty ,survey = "acs5", geometry = FALSE, output = "wide")
View(NC)
```

## Median Household Income

## Per Capital Income

## Rent Burden

## Unemployment -- 

## Race - Hispanic 

## Language 

## Age 

## Renters 

## Single Female household

## Single Parent household

## Household on public assistance

## Household without cars

## Education 

## Homeownership

## Housing units -- % mobile homes -- %

## Population 

## 
```{r}
write.csv(NC, paste(path ,"NCGrossRent.csv"), row.names = FALSE)
```


