

```{r}
options(scipen=999)
library(haven)
library(dplyr)
library(tidycensus)
library(janitor)
library(purrr)
```

```{r}
path = "C:/Users/padu/Desktop/UrbanInstitute/HousingChoiceVoucher/"
```

### Search

```{r}
Search <- load_variables(year = 2019, dataset = "acs5", cache = TRUE)
View(Search)
```

### Preview 

```{r}

Preview <- get_acs(geography = "tract", year = 2019, variables = "B17020_002", state = "NC", county = NCcounty ,survey = "acs5", geometry = FALSE, output = "wide")
View(Preview)

```


### Housing Choice Vouchers 

```{r}
#North Carolina Counties
NCcounty = lst(119,071,021,051,129,151,001,183,081)

#South Carolina Counties 
SCcounty = lst(045,083,007,019,079)

#Georgia Counties
GAcounty = lst(051, 245, 059, 121)

#Virginia Counties
VAcounty = lst(730, 015, 087, 810, 710)

#AllCounites 

AllCounties = lst(119,071,021,051,129,151,001,183,081,045,083,007,019,079,051, 245, 059, 121,
                  730, 015, 087, 810, 710)

#AllStates

AllStates = lst(37,45,51,13)
```


### AllCounties
```{r}
ACS <- get_acs(geography = "tract", year = 2019, variables = c(Totalrent = "B25063_001"), state = c("NC","SC", "VA", "GA"), county = AllCounties , geometry = FALSE, output = "wide")
View(ACS)
```
#### GrossRent

## North Carolina
```{r}
NC <- get_acs(geography = "tract", year = 2019, variables = c(Totalrent = "B25063_001"), state = "NC", county = NCcounty ,survey = "acs5", geometry = FALSE, output = "wide")
View(NC)
```

```{r}
write.csv(NC, paste(path ,"NCGrossRent.csv"), row.names = FALSE)
```



## South Carolina
```{r}
SC <- get_acs(geography = "tract", year = 2019, variables = c(Totalrent = "B25063_001"), state = "SC", county = SCcounty ,survey = "acs5", geometry = FALSE, output = "wide")
View(SC)
```

```{r}
write.csv(SC, paste(path ,"SCGrossRent.csv"), row.names = FALSE)
```


## Georgia
```{r}
GA <- get_acs(geography = "tract", year = 2019, variables = c(Totalrent = "B25063_001"), state = "GA", county = GAcounty ,survey = "acs5", geometry = FALSE, output = "wide")
View(GA)
```

```{r}
write.csv(GA, paste(path ,"GAGrossRent.csv"), row.names = FALSE)
```

## Virginia

```{r}
VA <- get_acs(geography = "tract", year = 2019, variables = c(Totalrent = "B25063_001"), state = "VA", county = VAcounty ,dataset = "acs5", geometry = FALSE, output = "wide")
View(VA)
```


```{r}

write.csv(VA, paste(path ,"VAGrossRent.csv"), row.names = FALSE)
```




```{r}
ACS2018 <- load_variables(year = 2019, dataset = "acs5", cache = TRUE)
View(ACS2018)
```

## Race 

#North Carolina 
```{r}
NCRace2019 <- get_acs(geography = "tract", year = 2019 , state = "NC", 
               county = NCcounty, variables = c(TotalRace = "B02001_001",
                                             WhiteAlone = "B02001_002",
                                             BlackorAfricanAmericanalone = "B02001_003",
                                             AmericanIndianandAlaskaNativealone = "B02001_004",
                                             Asianalone = "B02001_005",
                                             NativeHawaiianandOtherPacificIslanderalone = "B02001_006",
                                            Someotherracealone = "B02001_007",
                                            Twoormoreraces = "B02001_008",
                                            TwoormoreracesTworacesincludingSomeotherrace = "B02001_009",
                                            TworacesexcludingSomeotherraceandthreeormoreraces = "B02001_010"),
               survey = "acs5", output = "wide")
View(NCRace2019) 
```

```{r}
write.csv(NCRace2019, paste(path ,"NCRace2019.csv"), row.names = FALSE)
```

## South Carolina 
```{r}
SCRace2019 <- get_acs(geography = "tract", year = 2019 , state = "SC", 
               county = SCcounty, variables = c(TotalRace = "B02001_001",
                                             WhiteAlone = "B02001_002",
                                             BlackorAfricanAmericanalone = "B02001_003",
                                             AmericanIndianandAlaskaNativealone = "B02001_004",
                                             Asianalone = "B02001_005",
                                             NativeHawaiianandOtherPacificIslanderalone = "B02001_006",
                                            Someotherracealone = "B02001_007",
                                            Twoormoreraces = "B02001_008",
                                            TwoormoreracesTworacesincludingSomeotherrace = "B02001_009",
                                            TworacesexcludingSomeotherraceandthreeormoreraces = "B02001_010"),
               survey = "acs5", output = "wide")
View(SCRace2019) 
```

```{r}
write.csv(SCRace2019, paste(path ,"SCRace2019.csv"), row.names = FALSE)
```

## Georgia 
```{r}
GARace2019 <- get_acs(geography = "tract", year = 2019 , state = "GA", 
               county = GAcounty, variables = c(TotalRace = "B02001_001",
                                             WhiteAlone = "B02001_002",
                                             BlackorAfricanAmericanalone = "B02001_003",
                                             AmericanIndianandAlaskaNativealone = "B02001_004",
                                             Asianalone = "B02001_005",
                                             NativeHawaiianandOtherPacificIslanderalone = "B02001_006",
                                            Someotherracealone = "B02001_007",
                                            Twoormoreraces = "B02001_008",
                                            TwoormoreracesTworacesincludingSomeotherrace = "B02001_009",
                                            TworacesexcludingSomeotherraceandthreeormoreraces = "B02001_010"),
               survey = "acs5", output = "wide")
View(GARace2019) 
```

```{r}
write.csv(GARace2019, paste(path ,"GARace2019.csv"), row.names = FALSE)
```

## Virginia 

```{r}
VARace2019 <- get_acs(geography = "tract", year = 2019 , state = "VA", 
               county = VAcounty, variables = c(TotalRace = "B02001_001",
                                             WhiteAlone = "B02001_002",
                                             BlackorAfricanAmericanalone = "B02001_003",
                                             AmericanIndianandAlaskaNativealone = "B02001_004",
                                             Asianalone = "B02001_005",
                                             NativeHawaiianandOtherPacificIslanderalone = "B02001_006",
                                            Someotherracealone = "B02001_007",
                                            Twoormoreraces = "B02001_008",
                                            TwoormoreracesTworacesincludingSomeotherrace = "B02001_009",
                                            TworacesexcludingSomeotherraceandthreeormoreraces = "B02001_010"),
               survey = "acs5", output = "wide")
View(VARace2019) 
```

```{r}
write.csv(VARace2019, paste(path ,"VARace2019.csv"), row.names = FALSE)
```



### Median Household Income

## North Carolina 
```{r}
NCMI <- get_acs(geography = "tract", year = 2019 , state = "NC", 
               county = NCcounty, variables = c(MedianHouseholdIncome = "B19013_001",
                                             WhiteAloneMHI = "B19013A_001",
                                             BlackorAfricanAmericanaloneMHI = "B19013B_001",
                                             AmericanIndianandAlaskaNativealoneMHI = "B19013C_001",
                                             AsianaloneMHI = "B19013D_001",
                                             NativeHawaiianandOtherPacificIslanderaloneMHI = "B19013E_001",
                                            SomeotherracealoneMHI = "B19013F_001",
                                            TwoormoreracesMHI = "B19013G_001",
                                            WhiteAloneNotHispanicorLatinoMHI = "B19013H_001",
                                            HispanicOrLatinoMHI = "B19013I_001"
                                            ),
               survey = "acs5", geometry =FALSE, output = "wide")
View(NCMI) 
```

```{r}
write.csv(NCMI, paste(path ,"NCMedianHouseholdCome2019.csv"), row.names = FALSE)
```

## South Carolina
```{r}
SCMI <- get_acs(geography = "tract", year = 2019 , state = "SC", 
               county = SCcounty, variables = c(MedianHouseholdIncome = "B19013_001",
                                             WhiteAloneMHI = "B19013A_001",
                                             BlackorAfricanAmericanaloneMHI = "B19013B_001",
                                             AmericanIndianandAlaskaNativealoneMHI = "B19013C_001",
                                             AsianaloneMHI = "B19013D_001",
                                             NativeHawaiianandOtherPacificIslanderaloneMHI = "B19013E_001",
                                            SomeotherracealoneMHI = "B19013F_001",
                                            TwoormoreracesMHI = "B19013G_001",
                                            WhiteAloneNotHispanicorLatinoMHI = "B19013H_001",
                                            HispanicOrLatinoMHI = "B19013I_001"
                                            ),
               survey = "acs5", geometry =FALSE, output = "wide")
View(SCMI) 
```

```{r}
write.csv(SCMI, paste(path ,"SCMedianHouseholdCome2019.csv"), row.names = FALSE)
```


## Georgia 

```{r}
GAMI <- get_acs(geography = "tract", year = 2019 , state = "GA", 
               county = GAcounty, variables = c(MedianHouseholdIncome = "B19013_001",
                                             WhiteAloneMHI = "B19013A_001",
                                             BlackorAfricanAmericanaloneMHI = "B19013B_001",
                                             AmericanIndianandAlaskaNativealoneMHI = "B19013C_001",
                                             AsianaloneMHI = "B19013D_001",
                                             NativeHawaiianandOtherPacificIslanderaloneMHI = "B19013E_001",
                                            SomeotherracealoneMHI = "B19013F_001",
                                            TwoormoreracesMHI = "B19013G_001",
                                            WhiteAloneNotHispanicorLatinoMHI = "B19013H_001",
                                            HispanicOrLatinoMHI = "B19013I_001"
                                            ),
               survey = "acs5", geometry =FALSE, output = "wide")
View(GAMI) 
```

```{r}
write.csv(GAMI, paste(path ,"GAMedianHouseholdCome2019.csv"), row.names = FALSE)
```



## Virginia 

```{r}
VAMI <- get_acs(geography = "tract", year = 2019 , state = "VA", 
               county = VAcounty, variables = c(MedianHouseholdIncome = "B19013_001",
                                             WhiteAloneMHI = "B19013A_001",
                                             BlackorAfricanAmericanaloneMHI = "B19013B_001",
                                             AmericanIndianandAlaskaNativealoneMHI = "B19013C_001",
                                             AsianaloneMHI = "B19013D_001",
                                             NativeHawaiianandOtherPacificIslanderaloneMHI = "B19013E_001",
                                            SomeotherracealoneMHI = "B19013F_001",
                                            TwoormoreracesMHI = "B19013G_001",
                                            WhiteAloneNotHispanicorLatinoMHI = "B19013H_001",
                                            HispanicOrLatinoMHI = "B19013I_001"
                                            ),
               survey = "acs5", geometry =FALSE, output = "wide")
View(VAMI) 
```

```{r}
write.csv(VAMI, paste(path ,"VAMedianHouseholdCome2019.csv"), row.names = FALSE)
```


## Gini Income Index 

## North Carolina 

```{r}
NCGini <- get_acs(geography = "tract", year = 2019, variables = c(IncomeInequalityIndex = "B19083_001"), state = "NC", county = NCcounty ,survey = "acs5", geometry = FALSE, output = "wide")
View(NCGini)
```
```{r}
write.csv(NCGini, paste(path ,"NCIncomeInequality2019.csv"), row.names = FALSE)
```

## South Carolina 

```{r}
SCGini <- get_acs(geography = "tract", year = 2019, variables = c(IncomeInequalityIndex = "B19083_001"), state = "SC", county = SCcounty ,survey = "acs5", geometry = FALSE, output = "wide")
View(SCGini)
```

```{r}
write.csv(SCGini, paste(path ,"SCIncomeInequality2019.csv"), row.names = FALSE)
```

## Georgia 

```{r}
GAGini <- get_acs(geography = "tract", year = 2019, variables = c(IncomeInequalityIndex = "B19083_001"), state = "GA", county = GAcounty ,survey = "acs5", geometry = FALSE, output = "wide")
View(GAGini)
```

```{r}
write.csv(GAGini, paste(path ,"GAIncomeInequality2019.csv"), row.names = FALSE)
```
## Virginia 

```{r}
VAGini <- get_acs(geography = "tract", year = 2019, variables = c(IncomeInequalityIndex = "B19083_001"), state = "VA", county = VAcounty ,survey = "acs5", geometry = FALSE, output = "wide")
View(VAGini)
```

```{r}
write.csv(VAGini, paste(path ,"VAIncomeInequality2019.csv"), row.names = FALSE)
```

#Poverty

## North Carolina

```{r}
NCPov <- get_acs(geography = "tract", year = 2019, variables = c(BelowPoverty = "B17020_002",
                                                                 TotalPoverty = "B17020_010"), state = "NC", county = NCcounty ,survey = "acs5", geometry = FALSE, output = "wide")
View(NCPov)	


```
```{r}
write.csv(NCPov, paste(path ,"NCBelowPovertyLine.csv"), row.names = FALSE)
```


## South Carolina

```{r}
SCPov <- get_acs(geography = "tract", year = 2019, variables = c(BelowPoverty = "B17020_002",
                                                                 TotalPoverty = "B17020_010"), state = "SC", county = SCcounty ,survey = "acs5", geometry = FALSE, output = "wide")
View(SCPov)	

```

```{r}
write.csv(SCPov, paste(path ,"SCBelowPovertyLine.csv"), row.names = FALSE)
```

## Georgia 

```{r}
GAPov <- get_acs(geography = "tract", year = 2019, variables = c(BelowPoverty = "B17020_002",
                                                                 TotalPoverty = "B17020_010"), state = "GA", county = GAcounty ,survey = "acs5", geometry = FALSE, output = "wide")
View(GAPov)	

```

```{r}
write.csv(GAPov, paste(path ,"GABelowPovertyLine.csv"), row.names = FALSE)
```

## Virginia 

```{r}
VAPov <- get_acs(geography = "tract", year = 2019, variables = c(BelowPoverty = "B17020_002",
                                                                 TotalPoverty = "B17020_010"), state = "VA", county = VAcounty ,survey = "acs5", geometry = FALSE, output = "wide")
View(VAPov)	


```
```{r}
write.csv(VAPov, paste(path ,"VABelowPovertyLine.csv"), row.names = FALSE)
```


## LaborForce

### North Carolina

```{r}
NCLB <- get_acs(geography = "tract", year = 2019, variables = c(TotalLF = "B23025_001",
                                                                 CiviliansInLaborce = "B23025_003",
                                                                 InLaborForce = "B23025_002",
                                                                 UnemployedCivilians = "B23025_005",
                                                                 EmployedCivilians = "B23025_004"
                                                                 ), 
                 state = "NC", county = NCcounty ,survey = "acs5", geometry = FALSE, output = "wide")
View(NCLB)	


```
```{r}
write.csv(NCLB, paste(path ,"NCLaborFoce.csv"), row.names = FALSE)
```
## South Carolina 

```{r}
SCLB <- get_acs(geography = "tract", year = 2019, variables = c(TotalLF = "B23025_001",
                                                                 CiviliansInLaborce = "B23025_003",
                                                                 InLaborForce = "B23025_002",
                                                                 UnemployedCivilians = "B23025_005",
                                                                 EmployedCivilians = "B23025_004"
                                                                 ), 
                 state = "SC", county = SCcounty ,survey = "acs5", geometry = FALSE, output = "wide")
View(SCLB)	


```


```{r}
write.csv(SCLB, paste(path ,"SCLaborFoce.csv"), row.names = FALSE)
```
## Georgia

```{r}
GALB <- get_acs(geography = "tract", year = 2019, variables = c(TotalLF = "B23025_001",
                                                                 CiviliansInLaborce = "B23025_003",
                                                                 InLaborForce = "B23025_002",
                                                                 UnemployedCivilians = "B23025_005",
                                                                 EmployedCivilians = "B23025_004"
                                                                 ), 
                 state = "GA", county = GAcounty ,survey = "acs5", geometry = FALSE, output = "wide")
View(GALB)	


```

```{r}
write.csv(GALB, paste(path ,"GALaborFoce.csv"), row.names = FALSE)
```

## Virginia 

```{r}
VALB <- get_acs(geography = "tract", year = 2019, variables = c(TotalLF = "B23025_001",
                                                                 CiviliansInLaborce = "B23025_003",
                                                                 InLaborForce = "B23025_002",
                                                                 UnemployedCivilians = "B23025_005",
                                                                 EmployedCivilians = "B23025_004"
                                                                 ), 
                 state = "VA", county = VAcounty ,survey = "acs5", geometry = FALSE, output = "wide")
View(VALB)	


```

```{r}
write.csv(VALB, paste(path ,"VALaborFoce.csv"), row.names = FALSE)
```

## Renters 30%  of income above the poverty level 

## North Carolina

```{r}
NCRent30 <- get_acs(geography = "tract", year = 2019, variables = c(Income20000 = "B25106_028",
                                                                 Income200034999 = "B25106_032",
                                                                 Income35000949999 = "B25106_036",
                                                                 Income5000074999= "B25106_040",
                                                                 Income75000 = "B25106_044",
                                                                 NegativeIncome = "B25106_045"
                                                                 ), 
                 state = "NC", county = NCcounty ,survey = "acs5", geometry = FALSE, output = "wide")
View(NCRent30)
```
```{r}
NCRent30 <- NCRent30 %>% select(GEOID,NAME,Income20000E,Income200034999E,Income35000949999E,
                                Income5000074999E,Income75000E,NegativeIncomeE)
NCRent30
```

```{r}
NCRent30$RentBurden <- NCRent30$Income20000E + NCRent30$Income200034999E + NCRent30$Income35000949999E + NCRent30$Income5000074999E + NCRent30$Income75000E + NCRent30$NegativeIncomeE
```


```{r}
write.csv(NCRent30, paste(path ,"NCRentBurden.csv"), row.names = FALSE)
```

## South Carolina 

```{r}
SCRent30 <- get_acs(geography = "tract", year = 2019, variables = c(Income20000 = "B25106_028",
                                                                 Income200034999 = "B25106_032",
                                                                 Income35000949999 = "B25106_036",
                                                                 Income5000074999= "B25106_040",
                                                                 Income75000 = "B25106_044",
                                                                 NegativeIncome = "B25106_045"
                                                                 ), 
                 state = "SC", county = SCcounty ,survey = "acs5", geometry = FALSE, output = "wide")
View(SCRent30)
```
```{r}
SCRent30 <- SCRent30 %>% select(GEOID,NAME,Income20000E,Income200034999E,Income35000949999E,
                                Income5000074999E,Income75000E,NegativeIncomeE)
SCRent30
```

```{r}
SCRent30$RentBurden <- SCRent30$Income20000E + SCRent30$Income200034999E + SCRent30$Income35000949999E + SCRent30$Income5000074999E + SCRent30$Income75000E + SCRent30$NegativeIncomeE
```

```{r}
write.csv(SCRent30, paste(path ,"SCRentBurden.csv"), row.names = FALSE)
```


```{r}
GARent30 <- get_acs(geography = "tract", year = 2019, variables = c(Income20000 = "B25106_028",
                                                                 Income200034999 = "B25106_032",
                                                                 Income35000949999 = "B25106_036",
                                                                 Income5000074999= "B25106_040",
                                                                 Income75000 = "B25106_044",
                                                                 NegativeIncome = "B25106_045"
                                                                 ), 
                 state = "GA", county = GAcounty ,survey = "acs5", geometry = FALSE, output = "wide")
View(GARent30)
```

```{r}
GARent30 <- GARent30 %>% select(GEOID,NAME,Income20000E,Income200034999E,Income35000949999E,
                                Income5000074999E,Income75000E,NegativeIncomeE)
GARent30
```

```{r}
GARent30$RentBurden <- GARent30$Income20000E + GARent30$Income200034999E + GARent30$Income35000949999E + GARent30$Income5000074999E + GARent30$Income75000E + GARent30$NegativeIncomeE
```



```{r}
write.csv(GARent30, paste(path ,"GARentBurden.csv"), row.names = FALSE)
```


```{r}
VARent30 <- get_acs(geography = "tract", year = 2019, variables = c(Income20000 = "B25106_028",
                                                                 Income200034999 = "B25106_032",
                                                                 Income35000949999 = "B25106_036",
                                                                 Income5000074999= "B25106_040",
                                                                 Income75000 = "B25106_044",
                                                                 NegativeIncome = "B25106_045"
                                                                 ), 
                 state = "VA", county = VAcounty ,survey = "acs5", geometry = FALSE, output = "wide")
View(VARent30)
```
```{r}
VARent30 <- VARent30 %>% select(GEOID,NAME,Income20000E,Income200034999E,Income35000949999E,
                                Income5000074999E,Income75000E,NegativeIncomeE)
VARent30
```

```{r}
VARent30$RentBurden <- VARent30$Income20000E + VARent30$Income200034999E + VARent30$Income35000949999E + VARent30$Income5000074999E + VARent30$Income75000E + VARent30$NegativeIncomeE
```


```{r}
write.csv(VARent30, paste(path ,"VARentBurden.csv"), row.names = FALSE)
```